This aims to outline the System Development Life-Cycle (SDLC) of the
proposed project solution.
\newline \\ \\
\large \textbf{Overview of Implementation Phase}
\newline

Before implementations takes place, the development team will provide you (client) with the following documents:

\newline \\ \\
\textbf{Functional Requirements document}
    \begin{itemize}
         \item This document will address an in depth description of the Integrated Gynaecology Patient Information System, its primary and equivalent purpose of the system, set apart the functional and non-functional requirements of the system and its features, and the front end(which is the interface),and all the pre and post conditions that must be met when the system is working properly.
    \end{itemize}

\newline
\textbf{Architectural Design document}

    \begin{itemize}
         \item This document will address an in depth description of the Integrated Gynaecology Patient Information System, based on what architecture patterns that will be used and why?, that will be based on features each pattern provide which equivalent to meet the requirements of the system and its subsystem, and it will give an in depth understanding of the non-functional requirements in their priority order (which is critical, important and nice-to-have) 
    \end{itemize}
    
\newline

\textbf{Testing Document}
    \begin{itemize}
         \item This document will simply give a full report whether and the pre and post conditions of the system are met and shows whether the system works the way it is expected to.some of the usability goals include the following: 
\newline
\begin{itemize}
        \item  Effectiveness - is the product good at what it’s supposed to do?
        \item  Efficiency - does the product help to increase productivity?
        \item  Utility - does the product provide the functionality that the users
        want/need?
        \item  Learnability - is it easy to learn to use the product?
        \item  Intuitive - is it easy to use and understand? etc.
\end{itemize}
     \end{itemize}
     
\textbf{Included in all the above stipulated documentation will be:}
\begin{enumerate}
\item Unified Modelling Language (UML) diagrams to further illustrate the
flows, operations, sequences etc. that form part of the system's
operation.
\item Database Entity Relationship (ER) diagrams to illustrate the system entities that will form part of the system's persistent data.
\end{enumerate}

\textbf{Users’ and installation manual}
\newline
This document will provide a full description of how the system works to ensure effective usability of the system
