This aims to outline the System Development Life-Cycle (SDLC) of the
proposed project solution.
The project team will be submitting the following documents (further documentation to be included at a later stage):
\newline \\ \\
\textbf{Requirements Specification document}
    \begin{itemize}
         \item This document will provide a comprehensive description of the data lake.\\ \\ This requirement specification document will give a detailed description of the purpose of the system, system features and interfaces and formally stipulate the systems functional and non-functional requirements, its data requirements, quality requirements and the constraints under which it should operate.
    \end{itemize}

\newline
\textbf{Architectural Specification Document}

    \begin{itemize}
         \item This document will provide a comprehensive description of data lake system. This architectural specification will give a detailed view of the purpose of the data lake system with regard to its overall architecture and architectural features. This will then formally stipulate the subsystem views, policies, its data requirements, as well as the constraints under which the system operates.
    \end{itemize}
    
\newline

\textbf{Design Specification Document}
    \begin{itemize}
         \item This document will provide a design specification for the Data Lake system, which will
specify the design and layout of the system as specified in the related documents below. This design specification should help with the planning and implementation of a product which adheres to the following usability goals:
\newline
\begin{itemize}
        \item  Effectiveness - is the product good at what it’s supposed to do?
        \item  Efficiency - does the product help to increase productivity?
        \item  Utility - does the product provide the functionality that the users
        want/need?
        \item  Learnability - is it easy to learn to use the product?
        \item  Intuitive - is it easy to use and understand? etc.
\end{itemize}
     \end{itemize}
     
\textbf{Included in all the above stipulated documentation will be:}
\begin{enumerate}
\item Unified Modelling Language (UML) diagrams to further illustrate the
flows, operations, sequences etc. that form part of the system's
operation.
\item Database Entity Relationship (ER) diagrams to illustrate the system entities that will form part of the system's persistent data.
\end{enumerate}

\textbf{Users’ and installation manual}
\newline
These documents will provide detailed instructions of the installation and the
use of the system to ensure effective and efficient use of the system.
